---
title: "Homework 5"
author: "Laura Lynch, LL3255"
date: "11/11/2019"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(viridis)
library(dplyr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 10, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1
```{r}
# Load the data
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

### Function

* For numeric variables, you should fill in missing values with the mean of non-missing values
* For character variables, you should fill in missing values with "virginica"
```{r}
# takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector


# Apply this function to the columns of iris_with_missing using a map statement

```


# Problem 2

### Tidy Dataframe (containing data from all participants, including the subject ID, arm, and observations over time)

* Start with a dataframe containing all file names; the list.files function will help
* Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
* Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}

```

### Spagetti Plot (showing observations on each subject over time, and comment on differences between groups)

```{r}

```


# Problem 3

### Linear Regression Model

```{r}

```

* Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.
```{r}

```

* Make a plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis. Make a second plot (or overlay on the first) the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis. Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?
```{r}

```

